The impact of cosmic variance on simulating weak lensing surveys

### 2014-11-12 Writeup/paper_v3.tex
Reworded the statement about mass in S3

We also note that in Fig.~\ref{fig:median_sersicn}, the median \sersic
indices of the stellar mass-selected samples (\s$3$) are
systematically greater than those of the luminosity selected samples
(\s$1$, \s$2$).  We saw that \s3 is the smallest sample, and thus is
likely limited to higher mass galaxies overall.  It is therefore (\claire{Can't you show the masses are higer?} \arun{I am not sure what you want me to show here.}\claire{instead of saying the S3 sample is likely limited to higher mass galaxies, say it *is* limited to higher mass galaxies. You have the masses, so you don't have to hypothesize about the lower mass limit. I don't think you even need to give numbers, but I'd double check the statement is true by plotting the mass distributions for myself.}) not
surprising that it has a higher median \sersic $n$.  Finally, even for
the stellar mass-selected sample there is some sign of redshift
evolution.  The sign of this evolution is as expected, with lower
\sersic $n$ and $B/T$ for higher redshift samples, which should have a
higher fraction of disk and irregular galaxies and fewer galaxies with
bulge-like morphology.

>>>>

We also note that in Fig.~\ref{fig:median_sersicn}, the median \sersic
indices of the stellar mass-selected samples (\s$3$) are
systematically greater than those of the luminosity selected samples
(\s$1$, \s$2$).  
This is because \s3 is restricted to galaxies strictly above $\log(M/M_\odot) > 10.15$ where as in \s1 and \s2, the mass distribution of the galaxies extend till about $\log(M/M_\odot) \sim 9.0$.
It is therefore not surprising that it has a higher median \sersic $n$.  Finally, even for
the stellar mass-selected sample there is some sign of redshift
evolution.  The sign of this evolution is as expected, with lower
\sersic $n$ and $B/T$ for higher redshift samples, which should have a
higher fraction of disk and irregular galaxies and fewer galaxies with
bulge-like morphology.
